\textbf{Appendix}\\ A Thee-Step Approach for Assessing Landscape Connectivity via Simulated Dispersal: African Wild Dog Case Study

### 2022-02-07 Chapter_1/04_Manuscript/Manuscript_Support.tex
updates

%------------------------------------------------------------------------------
%	Appendix S1: Candiate Interactions
%------------------------------------------------------------------------------
\newpage
\section{Candidate Interactions}
We started with the base model and incrementally increased model complexity by
adding all possible two-way interactions between habitat covariates and movement
covariates. For instance, for the covariate \textsf{Water}, we proposed the
interactions \textsf{Water:sl}, \textsf{Water:log(sl)}, and
\textsf{Water:cos(ta)}. Besides these interactions, we also allowed for
correlations between turning angles and step lengths by proposing the
interactions \textsf{sl:cos(ta)} and \textsf{log(sl):cos(ta)}. Furthermore, we
formed the interactions \textsf{sl:LowActivity} and \textsf{log(sl):LowActivity}
to render that step lengths are likely to be shorter during periods of
inactivity.

@@

   upon which we based our movement model is depicted in the last row. We omitted
   all models with an AIC weight of zero from the table.}

>>>>

%------------------------------------------------------------------------------
%	Appendix S1: Candiate Interactions
%------------------------------------------------------------------------------
\newpage
\section{Candidate Interactions}
We started with the base model developed by \cite{Hofmann.2021} and
incrementally increased model complexity by adding all possible two-way
interactions between habitat covariates and movement covariates. For instance,
for the covariate \textsf{Water}, we proposed the interactions
\textsf{Water:sl}, \textsf{Water:log(sl)}, and \textsf{Water:cos(ta)}. Besides
these interactions, we also allowed for correlations between turning angles and
step lengths by proposing the interactions \textsf{sl:cos(ta)} and
\textsf{log(sl):cos(ta)}. Furthermore, we formed the interactions
\textsf{sl:LowActivity} and \textsf{log(sl):LowActivity} to render that step
lengths are likely to be shorter during periods of inactivity.

@@

  upon which we based our movement model is depicted in the last row and was
  originally presented in \cite{Hofmann.2021}. We omitted all models with an AIC
  weight of zero from the table.}
